This report documents the development, calibration, and business optimization of
an investment recommendation system for FinPUC, a fictitious financial advisory
platform that generates personalized portfolios for clients in the US stock
market. The system serves five risk profiles and pursues a dual objective:
maximizing client expected returns and maximizing firm revenue from transaction
fees.

The investment universe comprises 601 stocks filtered from 1,406 tickers.
Three methodological layers were implemented over two iterations. First,
Markowitz mean-variance optimization and four Black-Litterman view variants
were evaluated as baselines. Then, a sequential calibration framework over
three temporal horizons (calibration, validation, and clean test) was designed
to tune the Black-Litterman hyperparameters ($\tau$, $\Omega$, $P$, $Q$)
without contaminating the evaluation period. A business-parameter layer was
added to optimize the commission rate $K\% \in \{0.25\%, \dots, 5\%\}$ and the
multi-objective balance $\lambda \in [0,1]$ between client return and firm
utility, using 5,000 Monte Carlo trajectories over 260 weeks. Four view
families and three abandonment probability models (v1, v1$+$, v2) were compared
under identical validation protocols.

The sequential calibration converges to an unemployment-macro view with $\tau =
0.2$ and $\Omega$ confidence of 0.5, yielding a 3\% Sharpe improvement in
aggressive profiles with pandemic data. Among the views, general momentum
delivers the largest economic gain ($+85.7\%$ P4 score vs.\ Markowitz base,
$+5.2\%$ Sharpe) albeit with elevated turnover (34.6\%), while the
unemployment-macro view provides superior operational stability (7.3\%
turnover, HHI 0.157). The optimal commission rate and balance parameter are
identified via sensitivity and Pareto-frontier analysis, and the v1$+$
abandonment model with homogeneous ruin constraints is selected as the
recommended configuration for the final recommender.

\textbf{Keywords:} portfolio optimization, Markowitz, Black-Litterman
calibration, Monte Carlo simulation, recommender system, multi-objective
optimization, commission sensitivity, rolling validation, CVXPY.